Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
A cleaning pass on 3.2

To address additions and changes to the set of commands available to the shell, \sys provides command developers lightweight, domain-specific language (DSL).
The DSL allows developers to express semantic information about a command's distributanility that is critical to \sys.
This DSL can be used by the developers of new commands succinctly express this information, such the class of a command and the sequence of sources from which it reads its input.
It is also used by developers that work on existing commands to extend or maintain them, to express additions or changes to the command's semantics.

\heading{Command-line Options}
As described earlier~\sx{bg}, command-line options and environment variables can affect the operation of a command.
Options are a particularly popular way to control a command, 
  directly affecting a command's distributability classification.
That is, commands are assigned to default classes, and commands can change the class in which a command belongs.

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Distributability description language.}
\todo{The DSL attempts to capture important elements regarding the distributability aspects of various commands.}
\vspace{-20pt}
}

@@

\heading{Command Inputs and Outputs}
Consider the command \ttt{comm}. It takes as input two files and
implements some form of join. When invoked without any option, it
produces three-column output. The first column contains lines that
unique to the first file, the second column contains lines that are
unique to the second file, and the last column contains lines that
exist in both files. In the general case \ttt{comm} is pure, since it
needs to wait until it reads both files completely before it can
output its results.

However, \ttt{comm} can also be invoked using some options that
suppress the output of any combination of columns. More precisely, the
option \ttt{-1} suppresses the first column of the output. Similarly,
\ttt{-2} and \ttt{-3} supress the second and third column. Using both
\ttt{-2} (or \ttt{-1}) and \ttt{-3}, the command becomes stateless
regarding its first (resp. the second) file argument.

@@

\heading{Distributability DSL}
\sys's distributability description DSL (Fig.~\ref{fig:dsl}) is designed to be able to classify a commands into multiple categories given their options.

It assumes that the arguments of a command can always be separated to
options and file arguments (checking if they start with a
\ttt{-}~\footnote{Note that the single character \ttt{-} is not an
  option as it is most often used to designate that a command reads
  from its standard input}). A file written in the language contains a
record containing a mapping from predicates to assignments for each
command. Predicates can be simple boolean formulas on the existence
and the value of all options. Each assignment contains the command
category, the sequence of its input sources, and its output
source. Inputs to commands are a sequence of file arguments and its
standard input. Similarly, the output is either its standard output or
a file argument. An example record for comm can be seen below:

>>>>

To address additions and changes to the set of commands available to the shell, \sys provides command developers a lightweight, domain-specific language (DSL).
The DSL allows developers to express semantic information about a command's distributanility that is critical to \sys.
This DSL can be used by the developers of new commands to succinctly express this information, such the class of a command and the sequence of sources from which it reads its input.
It could also be used by developers that extend or maintain existing commands, to express additions or changes to the command's implementation or interface.

\heading{Command-line Options}
As described earlier~\sx{bg}, command-line options and environment variables can affect the operation of a command.
Options are a particularly popular way to control a command, 
  directly affecting a command's distributability classification.
That is, commands are assigned to default classes, and options can change the class in which they belong.

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Distributability description language.}
The DSL captures important information regarding the distributability of a command.
\vspace{-20pt}
}

@@

\heading{Command Inputs and Outputs}
%
Consider the command \ttt{comm}. It takes as input two files and
performs a join operation. When invoked without any option, it
produces three-column output. The first column contains lines that
unique to the first file, the second column contains lines that are
unique to the second file, and the last column contains lines that
exist in both files. In the general case \ttt{comm} is in \pur, since
it needs to wait until it reads both files completely before it can
output its results.

However, \ttt{comm} can also be invoked using some options that
suppress the output of any combination of columns. More precisely, the
option \ttt{-1} suppresses the first column of the output. Similarly,
\ttt{-2} and \ttt{-3} supress the second and third column. Using both
\ttt{-2} (or \ttt{-1}) and \ttt{-3}, the command becomes \sta
regarding its first (resp. the second) file argument.

@@

\heading{Distributability DSL}
%
\sys's distributability description DSL (Fig.~\ref{fig:dsl}) is
designed to be able to classify a commands into multiple categories
given their options.

It assumes that the arguments of a command can always be separated to
options and file arguments (checking if they start with a
\ttt{-}~\footnote{Note that the single character \ttt{-} is not an
  option as it is most often used to designate that a command reads
  from its standard input}). A file written in the language contains a
record containing a mapping from predicates to assignments for each
command. Predicates can be simple boolean formulas on the existence
and the value of any option. Each assignment contains the command
category, the sequence of its input sources, and its output
source. Inputs to commands are a sequence of file arguments and its
standard input. Similarly, the output is either its standard output or
a file argument. An example record for comm can be seen below:
